---
title: "`tirana`- Functions and design templates for Tiranas Municipality"
output: github_document
---

R package to bundle functions and document designs for work at Tirana Municipality Directorate of Transportation and Road Traffic  

# Installation 

To install the latest version from GitHub, run

```{r, eval = FALSE}
devtools::install_github("rcst/tirana")
```

To install the lastest release, install the package `drat` and the repo

```{r, eval = FALSE}
install.packages("drat")
drat::addRepo("rcst")
```

Now you can easily install it the usual way:

```{r eval = FALSE}
install.packages("tirana")
```

# Components

## `xaringan` presentation templates

### transport

A `xaringan` presentation template using the colors and fonts from [https://www.tirana.al](https://www.tirana.al), the template generates a QR-code (using package `qrencoder`) that can be included in any slide which can point to the URL of the presentation, when the parameter `www` is set to that URL

```
---
...
params:
   www: "https://www.yourwebsite.com/thispresentation.html"
...
---
```

To create a new presentation using this template, run

```{r, eval = FALSE}
rmarkdown::draft(file = "my_slides.Rmd", template = "transport", package = "tirana")
```

